% !TeX root = martinmadsenCV.tex
% !TEX program = xelatex

\documentclass{afriggeri-cv/friggeri-cv}

\defaultfontfeatures{Path=fonts/}
\usepackage{fontspec}
\usepackage{fontawesome}

\setmathfont{XITS Math}
\newfontfamily\bodyfont[]{LiberationSans-Regular}
\newfontfamily\thinfont[]{LiberationSans-Regular}
\newfontfamily\headingfont[]{LiberationSans-Bold}

\defaultfontfeatures{Mapping=tex-text}
\setmainfont[Mapping=tex-text, Color=textcolor,Path=fonts/]{LiberationSans-Regular}

\newcommand{\aau}{%
  Aalborg University (AAU), Denmark
}

\begin{document}
\header{martin}{madsen}
{software developer, \href{mailto:me@martinbjeldbak.com}{me@martinbjeldbak.com}}

\begin{aside}
  \section{about}
    melbourne
    australia
    \hfill
    32 years old
    \phone{+61 413 043 210}
    \website{martinbjeldbak.com}
    \github{martinbjeldbak}
    \linkedin{martinbjeldbak}
  \section{languages}
    danish, english
  \section{programming}
    Golang, Python
    Protocol Buffers, gRPC
    GitHub Actions
    Ruby on Rails
    SQL, Docker
    AWS, GCP
    \LaTeX, HTML, Git
    JavaScript, Python
    OS X, Unix
  \section{interests}
    continuous delivery
    machine learning
    devOps
    architecture
    web development
    self-hosting
  \section{other}
    Australian permanent resident
  \section{source}
    \github{martinbjeldbak/cv}
\end{aside}

\section{experience}

\begin{entrylist}
  \entry%
    {since 2020}
    {Software Engineer}
    {\href{https://www.anz.com.au}{ANZ Bank}, Melbourne, Australia}
    {Working on \href{https://www.anz.com.au/plus}{ANZ Plus} as software engineer. I have worked in multiple core teams at ANZ, initially focused on DevSecOps, then transitioning to data engineering in 2023. I work with architects, tech leads, and security team members to deliver features that support the bank across a multitude of areas. Main technologies used are Golang and gRPC, GitHub Actions, GCP services such as Dataflow, Pub/Sub, BigQuery, Spanner, and Cloud Run.}
  \entry%
    {2016--2020}
    {Lead Software Developer, Backend}
    {\href{https://netengine.com.au/}{NetEngine}, Brisbane, Australia}
    {Ruby on Rails software developer working with consultancy clients to build web-based systems across
      many different industries, from finance to flood mapping. I worked on setting up infrastructure
      in AWS to building GraphQL Rails APIs.
      I also partook in non-technical activities, such as business planning, training new backend developers. Clients include \href{https://netengine.com.au/project/apollo-motorhome-holidays/}{Apollo Motorhome Holidays}.}
  \entry%
    {2012--2014}
    {Student Software Developer}
    {\href{https://www.falck.com/services/healthcare}{Falck Healthcare a/s}, Aalborg, Denmark}
    {Development of Ruby on Rails-based system used daily by ca.\ 40 of Falck's physiotherapists to journal their patients' treatments and wellbeing.}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry%
    {2014--2016}
    {M.Sc.\ {\normalfont\ in Computer Science}}
    {\aau}
    {Majoring in Computer Science (120 ECTS)\\
    Specializing in Machine Intelligence}
  \entry%
    {2014--2015}
    {Studying abroad}
    {University of California, San Diego (UCSD), USA}
    {Fully accredited as part of the first year of my master's degree from Aalborg University}
  \entry%
    {2011--2014}
    {B.Sc.\ {\normalfont\ in Computer Science}}
    {\aau}
    {Majoring in Computer Science (180 ECTS)}
\end{entrylist}

\section{projects}
\begin{entrylist}
  \entry%
    {since 2025}
    {home-ops}
    {\github{martinbjeldbak/home-ops}}
    {running a 3-node Kubernetes cluster at home in a home lab, supporting media streaming and other workloads using Flux, Cilium, cert-manager, Renovate}
  \entry%
    {since 2024}
    {Shotta}
    {\github{martinbjeldbak/Shotta}}
    {World of Warcraft addon to take screenshots at user-defined intervals. Written in Lua. 1500+ downloads.}
  \entry%
    {2016}
    {A Hierarchical Tree Distance Measure for Classification}
    {\href{https://martinbjeldbak.com/thesis.pdf}{thesis.pdf}}
    {Concluded my M.Sc.\ degree. Published in \href{https://www.scitepress.org/Papers/2017/61985/}{Proceedings of the 6th International Conference on Pattern Recognition Applications and Methods~-~Volume 1: ICPRAM 2017, pages 502--509}}
\end{entrylist}
\end{document}
