\documentclass{afriggeri-cv/friggeri-cv}

\newcommand{\aau}{%
  Aalborg University (AAU), Denmark
}

\begin{document}
\header{martin}{madsen}
{software developer, me@martinbjeldbak.com}

\begin{aside}
  \section{about}
    502/25 Walsh Street
    Milton 4064
    Queensland
    Australia
    ~
    26 years old
    \phone{+61 413 043 210}
    \website{martinbjeldbak.com}
    \github{martinbjeldbak}
    \linkedin{martinbjeldbak}
  \section{languages}
    bilingual Danish/English
    IELTS score: 8.0
  \section{programming}
    Ruby on Rails
    Heroku, AWS, SQL
    \LaTeX, HTML, Git
    JavaScript (ES6, React)
    OS X, Unix
  \section{interests}
    machine learning
    TDD, functional programming
    service oriented architecture
    web development
\end{aside}

\section{experience}

\begin{entrylist}
  \entry%
    {since 2016}
    {Back-end Software Developer \& Project Manager}
    {\href{http://netengine.com.au/}{NetEngine}, Brisbane, Australia}
    {Ruby on Rails software developer working with our clients to build web-based systems across
      many different industries, from finance to flood mapping. I work on setting up infrastructure
      in AWS to building service objects in Rails and avoiding circular dependencies.}
  \entry%
    {2012-2014}
    {Student Software Developer}
    {\href{http://www.falck.com/en/company/organisation/business-areas/healthcare}{Falck Healthcare a/s}, Aalborg, Denmark}
    {Development of Ruby on Rails-based system used daily by ca.\ 40 of Falck's physiotherapists to journal their patients' treatments and wellbeing.}
  \entry
    {2010-2014}
    {Founder}
    {Divambu (shut down)}
    {Ran my own small company developing and hosting web sites for clients.}
\end{entrylist}

\section{education}

\begin{entrylist}
  \entry
    {2014-2016}
    {M.Sc.\ {\normalfont in Computer Science}}
    {\aau}
    {Majoring in Computer Science (120 ECTS)\\
    Specializing in Machine Intelligence}
  \entry
    {2014-2015}
    {Studying abroad}
    {University of California, San Diego}
    {Fully accredited as part of the first year of my master's degree from Aalborg University}
  \entry
    {2011-2014}
    {B.Sc.\ {\normalfont in Computer Science}}
    {\aau}
    {Majoring in Computer Science (180 ECTS)}
  \entry
    {2008-2011}
    {Student}
    {EUC Nord~-~Technical Gymnasium of Hjørring}
    {Focus in physics and engineering}
\end{entrylist}

\section{other activities}
\begin{entrylist}
  \entry
    {2013-2014}
    {Student member of the Study Board}
    {\aau}
    {Elected position. Handling of educations within Computer Science curricula at the university, quality assurance of education, handling of exemptions, etc.}
\end{entrylist}

\section{projects}
\begin{entrylist}
  \entry
    {2015}
    {XQuery Processor}
    {UC San Diego, \github{martinbjeldbak/xquery-processor}}
    {Implemented a subset of the XQuery and XPath XML query languages in Java}
  \entry
    {2016}
    {A Hierarchical Tree Distance Measure for Classification}
    {\href{http://martinbjeldbak.com/thesis.pdf}{martinbjeldbak.com/thesis.pdf}}
    {Concluded my M.Sc.\ degree. Published in \href{http://www.scitepress.org/DigitalLibrary/PublicationsDetail.aspx?ID=xSe8tY7QfHE=&t=1}{Proceedings of the 6th International Conference on Pattern Recognition Applications and Methods - Volume 1: ICPRAM}}
\end{entrylist}

\dots and many others! I contribute as much as I can to open source and work on other projects for fun. For more examples, feel free to check out my GitHub profile linked above.
\end{document}
